Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-01 Doc/Miccai/simulation.tex
Added annotations to the rest shape figure.
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@361 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\caption{Scheme showing the method for joining two vessels:  (a) the cut on vessel meshes is performed in a 3D geometry edition software. In the software, we impose that the number of the segments on the edges is the same on both side  (\color{BlueGreen}{$\mathbf{\rightarrow}$}\color{black})
Moreover, we select some shell elements that lie along the sutured edges (\color{purple}{$\mathbf{\rightarrow}$}\color{black}).
(b) In our software, we connect the vessel topologies by performing a relaxation of the shape and the rest shape for the selected shells.  
(c) We progressively re-contract the rest shape of the shells while computing the deformation of the whole unified mesh. 
In the final steady state computed in the simulation, the shell elements have all their correct rest shape.}
\label{fig-JoiningVessels}
\end{figure}

>>>>

\caption{Scheme showing the method for joining two vessels \stefan{Isn't that example too complex? I think it is really hard to actually see what is happening here. At least the colors have to be changed because the different layers are colored quite equally and it should be zoomed in to the interesting area were the joining takes place. Remember also that the procedings are printed in black and white and that everything must be visible when printing out this figure black and white. There must be way more contrast.}:  (a) the cut on vessel meshes is performed in a 3D geometry edition software. In the software, we impose that the number of the segments on the edges is the same on both side  (\color{BlueGreen}{$\mathbf{\rightarrow}$}\color{black})
Moreover, we select some shell elements that lie along the sutured edges (\color{purple}{$\mathbf{\rightarrow}$}\color{black}).
(b) In our software, we connect the vessel topologies by performing a relaxation of the shape and the rest shape for the selected shells.  
(c) We progressively re-contract the rest shape of the shells while computing the deformation of the whole unified mesh. 
In the final steady state computed in the simulation, the shell elements have all their correct rest shape.}
\label{fig-JoiningVessels}
\end{figure}
